\documentclass{scrartcl}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amssymb,amstext}
\usepackage{mathtools}

\usepackage[onehalfspacing]{setspace}

\begin{document}
	
	\title{Energy Online}
	\subtitle{}
	\author{J. Shah, M. Jordi, M. Stemmle, S. Oeschger, S. Zemljic}
	
	\maketitle
	\section{Introduction - Michael J. - around 600 words}
	\subsection{Context}
    \paragraph{}
    Please Check 01\_introduction.docx for the complete version with sources and footnotes.
    \paragraph{}
    The BIOTS program exists to push education for innovative new technologies into universities to help Switzerland o become one of the leading hubs in Blockchain and IoT space. 
    \paragraph{}
    Since 2016, every year the BIOTS program offers three major verticals for the students to build their ideas and use-cases. In 2018, the focus was on sustainability issues, which are currently on the agenda of the UN or hot topics in industry. Challenges from the sponsors Elektrizitätswerk der Stadt Zürich (EWZ), UBS Group AG (UBS), the European founded project FuturICT 2.0 (https://futurict2.eu) across the following verticals were presented and solved in the program:
    \paragraph{}
    -- PICTURE 01\_introduction\_picture01.PNG -- 
    (Figure 1: Major verticals of BIOTS 2018 , Source http://biots.org/the-biotsphere/)
    \paragraph{}
        This report was created as a result of the challenge 3 “virtual energy storage” from EWZ. 
    \subsection{Background}
    \paragraph{}
    In a cantonal vote 2017 it has been decided, that EWZ needs to sell all its holding in the nuclear sites of Gösgen and Leibstadt until 2034. In addition, EWZ will not be allowed to obtain nuclear energy anymore as well. 
    \paragraph{}
    In 2016 32.8\% of the electricity in Switzerland is provided by nuclear power plants.  To be able to cover those losses, massive investments into renewable energy are needed. Large power plants alone will not be enough to cover the demands, thus small-scale energy production, like private PV's will play a huge role. 
    \paragraph{}
    Currently, the entry barriers for the installation of PV are high, batterie storage for surplus energy is expensive and overall incentives are missing. For example, energy surplus from private power plants (mainly PV) can only be sold to local energy provider for a very low price of 8.50 Rp./kWh (high tariff) or 4.45 Rp./kWh (low tariff).  To incentivize the installation of PV, promotional money is lacking.   
    \paragraph{}
    To reach the goal of 0\% nuclear energy it is important to make private power plants more lucrative. Therefore, the challenge 3 of EWZ deals with the topic "Virtual Energy Storage". Virtual Energy Storage allows private household to store their surplus energy virtually and withdraw it later when needed. 
    \paragraph{}
    This concept has been already adapted   Companies like eOn or SENEC already offer services like this to their customers:
    \paragraph{}
    eOn (https://www.eon-solar.de/eon-solarcloud)
\begin{itemize}
\item Service Name: 		E.ON SolarCloud
\item Value Proposition: 	Genießen Sie jetzt Ihre Sonnenenergie 365 Tage, und Nächte
\item Value Chain:		E.ON -> End customer
\item Revenue Model: 	Monthly Fee
\item Customer Segment:	Private Households with PV installations
\end{itemize}
\paragraph{}
Senec-ies (https://www.senec-ies.com/tarife-services/senec-cloud/)
\begin{itemize}
\item Service Name:		SENEC.Cloud 2.0
\item Value Proposition:	Strom im Sommer einfrieren und im Winter wieder auftauen.
\item Value Chain:		SENEC -> End customer
\item Revenue Model: 	Monthly Fee
\item Customer Segment:	Private Households with PV installations
\end{itemize}


    Due to the companies and customers are thrusted parties in those two services offerings, the necessity of the blockchain technology is not given. According to Karl Wüst and Arthur Gervaisy, “Blockchain is being praised as a technological innovation which allows to revolutionize how society trades and interacts. This reputation is in particular attributable to its properties of allowing mutually mistrusting entities to exchange financial value and interact without relying on a trusted third party. A blockchain moreover provides an integrity protected data storage and allows to provide process transparency.” 

\subsection{Problem Statement}
 \paragraph{}
    The problem statement given by the EWZ Challenge 3 “Virtual Energy Storage” is: "How might the blockchain technology help to develop a reliable and highly efficient virtual energy solution that gives anyone the possibility to produce, store and use his/her own energy anywhere and anytime? " 
    \paragraph{}
    -- PICTURE 01\_introduction\_picture02.PNG -- 
    (Figure 2: EWZ Challenge 3 - "Virtual Energy Storage", Source: "BIOTS_ewz_challenges.pdf")
    \paragraph{}

	\section{Literature Review - Jig - around 1100 words}
    
    \begin{itemize}
    \item Business Model https://www.eon-solar.de/eon-solarcloud
    \item Business Model https://www.senec-ies.com/tarife-services/senec-cloud/
    \item Certificats: http://www.bfe.admin.ch/themen/00612/00614/index.html?lang=en
    \item Blockchain and Energy https://hbr.org/2017/03/how-utilities-are-using-blockchain-to-modernize-the-grid
    \item Blockchain and Energy https://www.etla.fi/wp-content/uploads/ETLA-Working-Papers-43.pdf
    \item Blockchain and Energy http://ieeexplore.ieee.org/abstract/document/7589035/
    \item .........
    \end{itemize}
	
	\section{Conceptual Model - Simon around 1100 words - Michael J. around 500 words}
	
	\paragraph{}
	Our aim is to create a Decentralised Autonomous Organisation (DAO). The DAO issues energy tokens for energy produced, witch can be traded freely through the blockchain network. The tokens can then be used to receive electricity again. The DAO uses the surplus energy in the network to trade on the energy stock market. With the profit from trading, new renewable power plants are subsidized. The DAO's behaviour is completely controlled by smart contracts.
	
	\paragraph{}
	The final goal is nothing less, than a complete disruption of the energy market. Electricity could be freely traded peer to peer, without the need of a controlling instance. The limitations through cantonal borders, would fall away, even trade across national borders could be possible at a later point. Current energy providers would take the role of a hardware provider, ensuring the maintenance of the energy grid and maybe the smart meters financed through fees for the usage of the infrastructure. 
	
	\subsection{Initialization through ICO}
	
	\paragraph{}
	At the beginning, there will be an "Initial Coin Offering" (ICO), to get the initial funds for the DAO and to distribute the tokens. A major part of the tokens will be sold to investors and given to energy producers. A smaller part could be distributed for example to core developers or held back as reserves. This process would give the DAO its starting capital to start investing in renewable energy, and then trade on the energy stock market. 
	\subsection{Decentralised Autonomous Organisation DAO}
	
	
	\paragraph{}
	A DAO's behaviour is defined by smart contracts. This includes how to invest in further power plants  and trading behaviour. With the surplus energy from the producing members the DAO trades on the energy stock market, according to the smart contracts. With the profit made from trading, the DAO pays subsidies to build renewable power plants and thus enlarging it's network. Mining happens on a proof of stake implementation, to keep energy consumption in check. 

    
   \section{Solution Design - Stefan - around 900 words}
   Coding: Architecture, modules etc.
   
   \section{Evaluation - Stefan - around 200 words}
	Features, Bugs etc.
	
    \section{Conclusion/Outlook - Michael S. - around 600 words}
	\paragraph{}
	A very important part are reliable measurements of energy production and consumption. It would be ideal, if smart meters could provide the data directly to the network. But it's highly possible that this does not work yet. As the trust in ewz is very high, and they already check energy consumption manually, this is a service ewz might provide.
	
	\paragraph{}
	Another problem might be on the legal front. The DAO is still a young concept with no laws existing yet. There is also the question, of how the certificates are handled in such a system.  
    
\end{document}