\documentclass{scrartcl}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amssymb,amstext}
\usepackage{mathtools}

\usepackage[onehalfspacing]{setspace}

\begin{document}
	
	\title{Energy Online}
	\subtitle{}
	\author{J. Shah, M. Jordi, M. Stemmle, S. Oeschger, S. Zemljic}
	
	\maketitle
	
	\section{The Problem}
	
	\paragraph{}
	With the acceptance of the "Energiestrategie 2050" it has been decided, that all nuclear plants in Switzerland have to go off the grid until 2034. Currently 40\% of the electricity in Switzerland is provided by nuclear power plants. To be able to cover those losses, massive investments into renewable energy are needed. Large power plants alone eill not be enough to cover the demands, thus small scale energy production, like private PV's will play a huge role.
	
	\paragraph{}
	Currently, energy surplus from private power plants (mainly PV) can only be sold to local energy provider for a fixed price. Combined with high entry barriers there is no real incentive to build private energy plants.
	To reach the goal of 0\% nuclear energy it is important to make private plants more lucrative and support them with subsidies. 
	
	\section{The Vision}
	
	\paragraph{}
	Our aim is to create a Decentralised Autonomous Organisation (DAO). The DAO issues energy tokens for energy produced, witch can be traded freely through the blockchain network. The tokens can then be used to receive electricity again. The DAO uses the surplus energy in the network to trade on the energy stock market. With the profit from trading, new renewable power plants are subsidized. Members of the DAO have a right to vote on changes in the DAO's smart contracts. The DAO's behaviour is completely controlled by those smart contracts.
	
	\paragraph{}
	The final goal is nothing less, than a complete disruption of the energy market. Electricity could be freely traded peer to peer, without the need of a controlling instance. Current energy providers would take the role of a hardware provider, ensuring the maintenance of the energy grid and maybe the smart meters financed through fees for the usage of the infrastructure. 
	
	\section{The way there}
	
	\subsection{Initialization through ICO}
	
	\paragraph{}
	At the beginning, there will be an "Initial Coin Offering" (ICO), to get the initial funds for the DAO and to distribute the tokens. A major part of the tokens will be sold to investors. A smaller part could be distributed for example to core developers or held back as reserves. This process would give the DAO its starting capital to start investing in renewable energy, and then trade on the energy stock market.
	
	\subsection{Decentralised Autonomous Organisation DAO}
	
	\paragraph{}
	A DAO's behaviour is defined by smart contracts. This includes how to invest in further power plants  and trading behaviour. Changes to these contracts can be decided by a majority of stakeholders. 
	
	\subsection{Difficulties}
	
	\paragraph{}
	A very important part are reliable measurements of energy production and consumption. It would be ideal, if smart meters could provide the data directly to the network. But it's highly possible that this does not work yet. As the trust in ewz is very high, and they already check energy consumption manually, this is a service ewz might provide.
	
	\paragraph{}
	Another problem might be on the legal front. The DAO doesn't fit in any corporate structure existing. 
	
\end{document}